Legion: Expressing Locality and Independence with Logical Regions

### 2012-04-30 doc/sc2012/circuit.tex

Lines 31-57 form the bulk of the actual simulation, performing three passes
over the circuit in each iteration.  Each pass loops over an array of pieces (constructed on lines 27-30 from the partitions),
spawning a task for each piece.   There are no explicit requests for
parallel execution (the default semantics of {\tt spawn} is sequential 
execution of the spawned tasks) nor is there synchronization required between the
passes.  Both the fact that the tasks can be run in parallel within a pass
and the required inter-pass dependencies are determined automatically
by the Legion runtime based on the region access annotations on the task declarations.
The  tasks spawned on lines 32-34 are {\em subtasks} of the main
{\tt simulate\_circuit} task. The region arguments to a subtask  must be either regions of, or subregions of, the arguments to its parent task with a subset of the permissions and the same coherence properties.  This restriction plays a central role in our task scheduling algorithm (see Section~\ref{sec:soop}).

>>>>

Lines 31-57 form the bulk of the actual simulation, performing three
passes over the circuit in each iteration.  Each pass loops over an
array of pieces (constructed on lines 27-30 from the partitions),
spawning a task for each piece.  There are no explicit requests for
parallel execution (the default semantics of {\tt spawn} is sequential
execution of the spawned tasks) nor is there synchronization required
between the passes.  Both the fact that the tasks can be run in
parallel within a pass and the required inter-pass dependencies are
determined automatically by the Legion runtime based on the region
access annotations on the task declarations.  The tasks spawned on
lines 32-34 are {\em subtasks} of the main {\tt simulate\_circuit}
task. A subtask can only take region arguments that are either also region arguments of or subregions
of region arguments of the parent task.  This requirement
plays an important role in our task scheduling algorithm (see
Section~\ref{sec:soop}).
